Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-10-20 04_paper/10_20_draft_newabstract.Rmd
started working on summary on methods

>>>>

# Methods

To test hypotheses 1-4 we rely on zero-inflated negative binomial regression models using yearly counts at the recipient-year level of the number of *Xinhua* article mentions and the number of bilateral diplomatic visits from Beijing as the response variables, respectively. Since these outcomes reflect discrete counts, we apply a method that explicitly models a discrete count process. We opt for negative binomial regression rather than Poisson since the variance of the outcomes is not equivalent to their means. We further apply the zero-inflated negative binomial model since the distributions of yearly coverage counts and visits contain a substantial number of zero values. Because of the panel nature of the data, we further include random recipient intercepts in model estimation to account for within-recipient dependence and additional unobserved recipient heterogeneity.

The first two specifications below model the yearly count of *Xinhua* mentions and of diplomatic visits from Beijing given the identity of the recipient country as one of either an aid beneficiary, a debtor, or both. These variables are denoted by a vector called "Type" which contains binary indicators for whether country $i$ in year $t$ receives exclusively aid, exclusively debt, or both from Beijing.

$$
\text{coverage}_{it} = \exp\{\tau_t + \text{Type}_{it}^\top \beta + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}; \tag{1}
$$

$$
\text{visits}_{it} = \exp\{\tau_t + \text{Type}_{it}^\top \beta + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}. \tag{2}
$$

These models are blunt tests of differences between coverage and visits for aid recipients and debtors relative to countries that receive neither from China. We additionally estimate the following two models to test whether changes in the amount of aid or debt received correspond to shifts in coverage and visits:

$$
\text{coverage}_{it} = \exp\{\tau_t + \beta_1 \text{ asinh}(\text{aid}_{it-1}) + \beta_2 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}; \tag{3}
$$

$$
\text{visits}_{it} = \exp\{\tau_t + \beta_2 \text{ asinh}(\text{aid}_{it-1}) + \beta_4 \text{ asinh}(\text{debt}_{it-1}) + X_{it} ^\top \gamma + \rho_i + \epsilon_{it} \}. \tag{4}
$$

Hypotheses 1-4 are tested via the direction and statistical significance of $\beta$ parameters 1-4. H1 (that aid recipients receive more outward facing coverage in *Xinhua*) will be supported if $\beta_1 > 0$ and H2 (that aid recipients host more diplomatic missions from Beijing) will be supported if $\beta_2 > 0$. H3 and H4 (hypotheses that parallel H1 and H2, but which apply to Chinese debt) will be supported if $\beta_3>0$ and $\beta_4>0$, respectively.

Models 1-4 each include year intercepts to adjust for yearly shocks and changes to Beijing's overall aid and debt portfolio, denoted by the term $\tau_t$. The parameter $\rho_i$ denotes random recipient intercepts. The vector $X_{it}$ denotes a set of control variables to improve precision and to adjust for possible confounders for Chinese bilateral financing, *Xinhua* coverage, and diplomatic visits. A summary of these variables, any transformations applied, and their sources is given in Table [x].

[Table x goes here]
